A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2020-03-30 paper/paper-revision.Rnw
Update deprecated code and add meeting notes (messy, to be fixed)

library(tidyverse)
library(magrittr)
library(tidyverse)
library(ggplot2)
library(keras)

@@

@@

@@

\fix{Rough idea: A reasonable criticism of this approach is that images from online retailers are of much higher quality than would be expected from the sidewalk scanner proposed earlier in this paper. This critique is especially fair considering that CNNs, and neural networks in general, have been shown to perform poorly on test data when it does not resemble the training data (find citation). However, this research is so new that we need to start somewhere. Once this work shows that CNNs can sufficiently distinguish outsole patterns/features, we can justify the effort to modify this approach for real/degraded images.}

@@

df_shoes_long <- df_shoes %>%
  tidyr::gather(key = feature, value = value, -str, -brand) %>%
  ungroup() %>%
  tidyr::nest(c(str, value)) %>%
  mutate(n_true = purrr::map_int(data, ~sum(.$value)),
         n_shoes_brand = purrr::map_int(data, ~length(.$value)))

>>>>

library(magrittr)
library(tidyverse)
library(tidyr)
nest <- nest_legacy
unnest <- unnest_legacy
library(ggplot2)
library(keras)

@@

\fix{We are working to dev a scanner using photo technology. It takes pics like Zappos. While images are degraded in some ways, the fundamental reqs are sim. We want to dev the methodology for this before we get actual data.}

\fix{manual collection citations: presentation by Sandy Parent, benedict et al, benedict cites another, the one that says college students and criminals are basically the same}

@@

\mt{subsection: motivation (w/ pics of scanner)}

@@

\fix{Rough idea: A reasonable criticism of this approach is that images from online retailers are of much higher quality than would be expected from the sidewalk scanner proposed earlier in this paper. This critique is especially fair considering that CNNs, and neural networks in general, have been shown to perform poorly on test data when it does not resemble the training data (find citation). However, this research is so new that we need to start somewhere. We need to work the kinks out of recognizing characteristics that examiners use. We can do that on real data once the scanner has been built and once we know how well our classification works. AKA find the pitfalls for clean images rather than introduce too many points of failure at once. Once this work shows that CNNs can sufficiently distinguish outsole patterns/features, we can justify the effort to modify this approach for real/degraded images.}

@@

df_shoes_long <- df_shoes %>%
  tidyr::gather(key = feature, value = value, -str, -brand) %>%
  ungroup() %>%
  tidyr::nest_legacy(c(str, value)) %>%
  mutate(n_true = purrr::map_int(data, ~sum(.$value)),
         n_shoes_brand = purrr::map_int(data, ~length(.$value)))
